Quantum Hoare Type Theory

### 2020-10-25 ms-paper/ms-paper.tex
Reduce dependence on QIO

\begin{abstract}
	% Foreward
	%Context and Need
	As quantum computers become real, it is high time we come up with effective techniques that help programmers write correct quantum programs.
	%Need
	In classical computing, formal verification and sound static type systems prevent several classes of bugs from being introduced. There is a need for similar techniques in the quantum regime.
	%Task
	Inspired by Hoare Type Theory in the classical paradigm, we propose Quantum Hoare Types by extending the Quantum IO Monad by indexing it with pre- and post-conditions that serve as program specifications.
	%Object
	In this paper, we introduce Quantum Hoare Type Theory (QHTT), present its syntax and typing rules, and demonstrate its effectiveness with the help of examples.
	% Summary
	%Findings

@@

As programming languages researchers, we think it will be better to encode such assertions into a static type system both for formal verification and to aid the programmers in writing correct programs from the start. Inspired by the use of Hoare triples in the verification of imperative programs and building on the idea of Hoare Type Theory (HTT) for classical programming languages~\cite{nanevski_hoare_2008}, we extend the Quantum IO Monad interface~\cite{qio} and propose Quantum Hoare Type Theory aimed at enabling both sound static type checking and formal verification of quantum programs.

>>>>

\begin{abstract}
	% Foreward
	%Context and Need
	As quantum computers become real, it is high time we come up with effective techniques that help programmers write correct quantum programs.
	%Need
	In classical computing, formal verification and sound static type systems prevent several classes of bugs from being introduced. There is a need for similar techniques in the quantum regime.
	%Task
	Inspired by Hoare Type Theory in the classical paradigm, we propose Quantum Hoare Types in which a quantum effect monad is indexed with pre- and post-conditions that serve as program specifications.
	%Object
	In this paper, we introduce Quantum Hoare Type Theory (QHTT), present its syntax and typing rules, and demonstrate its effectiveness with the help of examples.
	% Summary
	%Findings

@@

As programming languages researchers, we think it will be better to encode such assertions into a static type system both for formal verification and to aid the programmers in writing correct programs from the start. Inspired by the use of Hoare triples in the verification of imperative programs and building on the idea of Hoare Type Theory (HTT) for classical programming languages~\cite{nanevski_hoare_2008}, we extend a quantum effect monad inspired by the Quantum IO Monad interface~\cite{qio} and propose Quantum Hoare Type Theory aimed at enabling both sound static type checking and formal verification of quantum programs.
